### 2013-05-17 poster/poster.tex
chris edit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Main Features%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Features}{name=features,column=0,span=1.15,below=abstract}{
For our classification model, we use the \texttt{creg} \\\url{https://github.com/redpony/creg}
%\linebreak

\begin{description}
\item [Part-of-speech (POS) $n$-grams] Counts of every POS 1-, 2-, and 3-gram in each document. %53.92\% 
\item [FreqChar] Counts of character $n$-grams that are observed more than 5 times in the training corpus. $n$ ranges from~1 to~4.
\item [CharPrompt] Conjunction of the FreqChar features with the prompt ID %65.09
\item [Brown clusters] We clustered 8~billion words of English into 600~clusters of words that appear in similar left and right contexts. (\url{http://www.ark.cs.cmu.edu/cdyer/en-600/cluster_viewer.html}). Our features are counts of $n$-grams of Brown clusters as lexical representations. $n$ ranges from~1 to~4.
\item[PsvRatio] The proportion of passive verbs out of all verbs.
\item[DocLen] Document length in tokens.
\item[Punct] Counts of each punctuation mark. 
\item[Misspell] Spelling correction edits. Features included substitutions, deletions, insertions and joinings (\textnl{alot}$\rightarrow$\textnl{a lot}) that were made by the author of the essay. High-weight features include: {\tt ARA:DEL<e>}, {\tt ARA:INS<e>}; {\tt GER:SUBST<z>/<y>}; {\tt JPN:SUBST<l>/<r>}, {\tt JPN:SUBST<r>/<l>}; {\tt SPA:INS<s>}.% as well as the word position where the error occurred.
\item[\feat{Restore}] Counts of substitutions, deletions and
  insertions of predefined tokens that we restored in the texts: {\tt CHI:DELWORD<do>}; {\tt GER:DELWORD<on>}.%; {\tt ITA:DELWORD<be>} 
\item[CxtFxn] Contextual function words. Counts of $n$-grams consisting of one or two function words and the POS tag of the adjacent words: {\tt CHI:<some JJ>}; \mbox{\tt HIN:<as VBN>}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Model}{name=model,column=0,span=1.15,below=abstract}{
We use a logistic regression model implemented by \texttt{creg} trained to maximize log-likelihood, penalized by a combined $\ell_2$ and entropic regularizer.
\begin{align*}
\hat{\boldsymbol{\lambda}} = \arg \min_{\boldsymbol{\lambda}} \alpha \overbrace{\sum_j \lambda_j^2}^{\textrm{$\ell_2$ reg.}} - \sum_{\{(\textbf{x}_i,y_i )\}_{i=1}^{|\mathcal{D}|}} \Big(& \overbrace{\log p_{\boldsymbol{\lambda}}(y_i \mid \textbf{x}_i)}^{\textrm{log likelihood}}  + \\
& \vspace{-1cm} \tau \underbrace{\mathbb{E}_{p_{\boldsymbol{\lambda}}(y' \mid \textbf{x}_i)} \log p_{\boldsymbol{\lambda}}(y' \mid \textbf{x}_i)}_{-\textrm{conditional entropy}}\Big)
\end{align*}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%Main Features%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Features}{name=features,column=0,span=1.15,below=model}{
%\linebreak

\begin{description}
\item [Part-of-speech (POS) $n$-grams] Counts of every POS 1-, 2-, and 3-gram in each document. %53.92\% 
\item [FreqChar] Counts of character 1--4-grams that are observed more than 5 times in the training corpus.
\item [CharPrompt] Conjunction of the FreqChar features with the prompt ID %65.09
\item [Brown clusters] We clustered 8~billion words of English into 600~clusters and used 1--4-grams.
\item[PsvRatio] The proportion of passive verbs out of all verbs.
\item[DocLen] Document length in tokens.
\item[Punct] Counts of each punctuation mark. 
\item[Misspell] Spelling correction edits. Features included substitutions, deletions, insertions and joinings.% as well as the word position where the error occurred.
\item[\feat{Restore}] Substitutions, deletions and
  insertions of common words that were restored with an $n$-gram LM.
\item[CxtFxn] Contextual function words. Counts of $n$-grams consisting of one or two function words and the POS tag of the adjacent words: {\tt CHI:<some JJ>}.
